Title

### 2019-07-08 4_method.tex
extended gMAT figure ewith voronoi
fix figure which was initialized wrongly
MAT intro

\subsection{Medial Axis}
In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
There are several possible skeletonal structures we could consider.

\subsubsection{In related literature}

@@

\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, thethe feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''

\cite{kao1998optimal}
\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{MAT explanation by Kao et al.}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{gMAT}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
\caption{Quads in gMAT}
\end{subfigure}
\caption{Grounded medial axis transform. Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple. The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
\label{gmat}
\end{figure}

>>>>

\subsection{Skeletonization}
In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
There are several possible skeletonal structures we could consider.

\subsubsection{Background}
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
See \cref{MAT_explanation}.

@@

The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
The MAT can unambiguously recreate the exact input shape. \todo{[citation needed]}

\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''

The medial axis of a polygonal shape is a subset of the voronoi diagram generated on the line segments of the shape. \todo{[citation needed]}

\begin{figure}
\centering
\includegraphics[width=.9\columnwidth]{sources/intro/medial_axis_Kao.png}
\caption{MAT explanation by \citeauthor{kao1998optimal}}
\label{MAT_explanation}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
\caption{MAT}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
\caption{Voronoi}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
\caption{gMAT}
\end{subfigure}
\begin{subfigure}{0.24\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
\caption{Quads}
\end{subfigure}
\caption{Grounded medial axis transform. Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple. The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
\label{gmat}
\end{figure}
